\section{4th Iteration}
The 4th iteration is where the 2nd release where completed.

Step Counter \\
Settings GUI/Activity


\subsection{2nd Release}
With the basic music plater application completed in the 2nd iteration we outlined the configuration for the 3rd and 4th iterations in the configuration table seen in \ref{table:config1} taken from \citet{essence:config}.


\input{Content/Iteration/configurationTable1}

\begin{itemize}
\item Paradigm Focus: The challenge is to improve running experience by matching music beat to pace. The application is supposed to be used while running.
\item Paradigm Overview: Stakeholder is the user who is using the application.
\item Paradigm Details: For this release we have a two main scenarios to fulfil. First we want the application to automatically select appropriate (songs with a matching beat) songs to play as the user runs at varying paces. The song pool to select from should be customisable for each device.
\item Product Focus: The application is first and foremost a running pace, meaning the purpose is to match music beat with steps per minute (pace). It is possible to add an option for interval training so the application no longer adapt music beat based on pace, but encourage the user to adapts his or her pace to predetermined intervals of low and high beat music. Additional training programs could also be added. Further more the application can also server as a step counter not playing any music just recording steps taken and displays steps per minute, and the other way around just playing music without taking steps per second into account.
\item Product Overview: The application design should be based on a ``familiar music player design'', it should have the expected functionally from a music player and new elements (such as steps per minute) should expand on the familiar design. 
\Kristian{consider ``familiar music player design''}
\item Product Details: This configuration consists of 3 components the music player, a library and a step counter. The music player is used to play songs and serve as the primary interface for the user. The music library is one or more folders with MP3 files on the device. The step counter makes use of the device's accelerometer to register steps taken.
\item Project Focus: The overall vision of the application is as a running pacer which matches the beat of songs to played with running pace.
\item Project Overview: Grounds are described in \cref{chap:intro}.
\item Project Details: \Kristian{this seems similar to \textit{Affordance}}
\item Process Focus: The evaluation is based on benefits to the user(runner).
\item Process Overview: We evaluate the application as a surrogate customer at iteration end/review. The evaluation is based on the fulfilment of acceptance tests.
\item Process Details: 

\end{itemize}