\subsection{Review 4}
\paragraph{23rd March - 10th April}


Summary of extended meeting at the bottom of this document.

\textbf{Estimations:}
\begin{itemize}
\item We expected to work 70 hours, 67 hours on code and 3 hours on report. It turned out we worked 71 hours in total, 68 hours on code and 3 hours on report. This estimation is concluded to be spot on, as the measurements have small variations, which can make up for the extra hour.
\item We have solved issues for 82 estimated hours in this iteration (non report only, nor extra bug fixed (4 hours)).
\item Based on estimations of the issues of the iteration, we can conclude that when an issue is estimated between 8 (10) and 20 hours, the time actually used is approximately 60\% of the estimated time. However when we estimate non-trivial short issues (2-4 hours) we estimate fairly low in comparison to the actual used time. i.e. two issues estimated to 2 hours took 8 hours and 3,5 hours respectively.
\item The small deviation in time between estimated and actual used time, can be traced to the granularity of our estimations. We have a granularity where we estime in actual hours in up to 2 hours. More than 2 hours are estimated in units of half a day. 4 hours are half a day, 8 hours are an entire day, 10 hours are a day and a half … We used these numbers because of the restrictions of the online planning poker tool used.
This actually works okay, as it gives the opportunity to estimate trivial issues to less than half a day, which obviously will give a lot of overhead.

\end{itemize}
\Ivan{Good reflections and good section.}
\textbf{What Did We Accomplish?}
\begin{itemize}
\item We finished the step counter
\item We fixed the out-of-memory issue with the album covers.
\item We created the GUI for settings and SongScanner.
\item We fixed a number of small bugs.
\begin{itemize}
\item Next song after completion.
\item Handle missing songs.
\item Stop button skipped to next song.
\item Set filename as song title if no other title is available from the MP3 file itself 
\end{itemize}
\item We now only need the following to finish our MVP
\begin{itemize}
\item Acceptance tests
\item Control without looking at screen
\item Finish BPM online tests
\item General unit tests
\item Settings for the step counter, i.e. sensitivity
\item Refactoring. Modulation, and correct encapsulation.
\end{itemize}
\end{itemize}

\textbf{Status on Master}
\begin{itemize}
\item Working and tested
\begin{itemize}
\item Step Counter
\item Music Player
\item Song Scanner
\end{itemize}
\end{itemize}

\begin{itemize}
\item Issues still on master
	\begin{itemize}
	\item Step Counter
		\begin{itemize}
		\item Works as intended
		\end{itemize}
	\end{itemize}
	\begin{itemize}
	\item Music Player
		\begin{itemize}
		\item Invalid state exceptions still happen on master (warnings in log)
		\item prev and next pauses song when playing, it should continue playing the new song.
		\item Seekbar seekTo functions correctly, but have display issues jumps when dragging.
		\end{itemize}
	\end{itemize}
	\begin{itemize}
	\item Song Scanner
		\begin{itemize}
		\item Missing online BPM lookup in Song Scanner.
		\item Song Scanner Settings not used in app.
		\end{itemize}
	\end{itemize}
\end{itemize}
