\subsection{Review 5}
\paragraph{13th April - 24th April}

\textbf{Plan:}
\begin{itemize}
\item Use the length for each unit in hours instead of the hours used in planning poker.
\item Based on experience, 70 hours an an itera of work each iteration. continue to plan 70 hours of work each iteration. continue to plan 70 hours of work each iteration.
\end{itemize}

\begin{table}[h]
\begin{tabular}{|c|c|}
\hline
Estimated Planning Poker Time & Time Allocated in Project and Github     \\ \hline
0 hours                       & N/A                                      \\ \hline
0.5 hours                     & N/A                                      \\ \hline
1 hours                       & 1 hour (min estimate, trivial)           \\ \hline
2 hours                       & N/A                                      \\ \hline
3 hours                       & 1 Unit - Half a day - 3 hours            \\ \hline
5 hours                       & N/A                                      \\ \hline
8 hours                       & 2 Units - a day - 6 hours                \\ \hline
13 hours                      & 3 Units - a day and a half - 9 hours     \\ \hline
20 hours                      & 4 Units - two days - 12 hours            \\ \hline
40 hours                      & 5 Units - two and a half days - 15 hours \\ \hline
100 hours                     & 6 Units - three days - 18 hours          \\ \hline
??                            & Unknown                                  \\ \hline
\end{tabular}
\end{table}

Summary of extended meeting at the bottom of this document.

\textbf{Estimations:}
\begin{itemize}
\item We did not really estimate anything this iteration.
\item We forgot to track the time used for most of the iteration. This was because we refactored loosely and did not create issues for all assignments.
\item We used a lot of time on review of retrospective of last iteration, this should be tracked and estimated as well.
\end{itemize}


\textbf{What Did We Accomplish?}
\Ivan{Elaborate on symptoms and diagnosis. What went wrong? Why did it go wrong?}
\begin{itemize}
\item Overall this iteration was much less productive than planned - we expected the more “boring” tasks to result in less productivity, but we were unable to handle it in a satisfying way.
\item We made a refactoring plan, ensuring somewhat similar refactoring patterns.
\item We refactored a small part of the program.
\item We fixed (worked around) a periodic bug because the cover flow hangs, which we solved by just turning off the screen. \Ivan{Ugly, but okay that we write it. Either describe symptoms and diagnosis or just say ``Okay, we are busy, so in this version, we have this bug with a todo, although it is quick and dirty''.}
\item We discovered that we have not quite tested well enough. \Ivan{Elaborate}
\item All in all we have been VERY VERY unproductive and have been too easily distracted.
\end{itemize}


\textbf{Status on Master}
\begin{itemize}
\item Some issues were resolved on master
\begin{itemize}
\item online BPM
\item periodic crash doing tests
\end{itemize}
\end{itemize}

\begin{itemize}
\item Issues still on master
	\begin{itemize}
	\item Music Player
		\begin{itemize}
		\item prev and next pauses song when playing, it should continue playing the new song.
		\item Seekbar seekTo functions correctly, but have display issues jumps when dragging.
		\end{itemize}
	\end{itemize}
	\begin{itemize}
	\item Song Scanner
		\begin{itemize}
		\item Song Scanner Settings not used in app.
		\end{itemize}
	\end{itemize}
	\begin{itemize}
	\item Tests are incomplete
		\begin{itemize}
		\item BPM in DB not tested
		\end{itemize}
	\end{itemize}
\end{itemize}
